Open source landscape ecology tools

### 2020-07-20 paper/paper.Rmd
Fixing typo in email

---
title: Open source landscape ecology tools
# subtitle: Do you have a subtitle? If so, write it here
# titlerunning: Open source landscape ecology tools
# authorrunning: Short form of author list if too long for running head
thanks: | 
    Grants or other notes about the article that should go on the front 
    page should be placed here. General acknowledgments should be placed at the
    end of the article.
authors: 
- name: Maximillian H.K. Hesselbarth
  address: Department of Ecosystem Modelling, University of Goettingen, Buesgenweg 4, 37077 Goettingen, Germany
  email: mhk.hesselbarthh@gmail.com
- name: Jakub Nowosad
  address: Institute of Geoecology and Geoinformation, Adam Mickiewicz University, Krygowskiego 10, 61-680 Poznan, Poland
  email: nowosad.jakub@gmail.com
- name: Author 3
  address: Adress author 3
  email: E-Mail author 3
- name: ...
  address: ...
  email: ...
keywords:
- keyword 1
- keyword 2
- keyword 3
- keyword 4
- ...
abstract: |
  max. (200 words) Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract
bibliography: bibliography.bib
bibstyle: spphys # bibstyle options spbasic(default), spphys, spmpsci
preamble: | 
  \usepackage{caption}
  \usepackage{ltablex}
  \usepackage{lscape}
  \usepackage{multirow}
output:
  bookdown::pdf_book:
    base_format: rticles::springer_article
    number_sections: yes
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: Open source landscape ecology tools
# subtitle: Do you have a subtitle? If so, write it here
# titlerunning: Open source landscape ecology tools
# authorrunning: Short form of author list if too long for running head
thanks: | 
    Grants or other notes about the article that should go on the front 
    page should be placed here. General acknowledgments should be placed at the
    end of the article.
authors: 
- name: Maximillian H.K. Hesselbarth
  address: Department of Ecosystem Modelling, University of Goettingen, Buesgenweg 4, 37077 Goettingen, Germany
  email: mhk.hesselbarth@gmail.com
- name: Jakub Nowosad
  address: Institute of Geoecology and Geoinformation, Adam Mickiewicz University, Krygowskiego 10, 61-680 Poznan, Poland
  email: nowosad.jakub@gmail.com
- name: Author 3
  address: Adress author 3
  email: E-Mail author 3
- name: ...
  address: ...
  email: ...
keywords:
- keyword 1
- keyword 2
- keyword 3
- keyword 4
- ...
abstract: |
  max. (200 words) Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract
bibliography: bibliography.bib
bibstyle: spphys # bibstyle options spbasic(default), spphys, spmpsci
preamble: | 
  \usepackage{caption}
  \usepackage{ltablex}
  \usepackage{lscape}
  \usepackage{multirow}
output:
  bookdown::pdf_book:
    base_format: rticles::springer_article
    number_sections: yes
editor_options: 
  chunk_output_type: console
---
